### 2025-08-05 sec/related-work.tex
update literature

\begin{itemize}
\item Transparent visualisations \cite{perera22,bond24}
\end{itemize}

>>>>

\begin{itemize}
    \item Transparent visualisations \cite{perera22,bond25,psallidas18smoke}
    \item recent advances in interpretable language understanding, highlighting the shift from fine-tuning to prompt-based learning in NLP and presenting research on improving the transparency of neural models through interpretable classifiers, uncertainty analysis, and explainable systems. \cite{Yulan_2023}
    \item Quantity extraction in scientific text \cite{bolucu-etal-2023-investigating}
    \item Scientific fact checking \cite{abu-ahmad-etal-2025-climatecheck-shared}

\end{itemize}
